%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Arthur Lolos
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Arthur Lolos}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    528 MacArthur Ave.                             \hfill tel.: +1 973 572 7102              \vspace{0mm}\\\vspace{0mm}%
    Garfield, NJ 07026                       \hfill email: art.lolos1@gmail.com              \vspace{0mm}\\\vspace{0mm}%

    %__________________________________________________________________________________________________________________
    % Objective
    \section{\mysidestyle Objective}
    To obtain a Linux systems administration / engineering / devops position.


    %__________________________________________________________________________________________________________________
    % Skills
    \section{\mysidestyle Skills}

    \begin{itemize}
    \item Ability to correlate historical data with observational phenomena for root cause analysis
    \item Familiar with the UNIX shell, commandline utilities (ping, curl, wget, top, sar, etc.)
    \item Web development experience using python and mysql
    \end{itemize}
    

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}
    \textbf{Consulting} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Linux Systems Engineering Intern} \hfill \textbf{2013}\\
    Maintained uptime for various websites under contract.

    \textbf{Shoprite Pharmacy}, Lodi, NJ \vspace{2mm}\\\vspace{1mm}%
    \textsl{Pharmacy Technician} \hfill \textbf{2008 -- November 2013}\\
    Processed high volume of order requests from nurses, doctors and pharmacists over the phone.\\
    Responsible for entry of new patient profiles and prescriptions into local database.\\
    Maintained critical logging, storage, security and inventory of medication.\\
    Ensured the proper functionality and maintenance of critical laboratory equipment.\\
    Accurately recorded compounded products and prepared appropriate labels.

    \textbf{Dr. Maria Ramos}, Lodi, NJ \vspace{2mm}\\\vspace{1mm}%
    \textsl{Office Manager} \hfill \textbf{December 2011 -- April 2012}\\
    Shepherded patients, providing proper triage and prioritization and juggled scheduling conflicts.\\
    Handled organization of electronic patient records under HIPPA privacy guidelines.\\
    Managed office technology and acted as functional in-house IT staff for small office.

    \textbf{Picture People}, Paramus, NJ \vspace{2mm}\\\vspace{1mm}%
    \textsl{Photographer / Sales Representative} \hfill \textbf{2006 -- 2007}\\

    \textbf{Starbucks}, Hasbrouck Heights, NJ \vspace{2mm}\\\vspace{1mm}%
    \textsl{Barista} \hfill \textbf{2005 -- 2006}\\


    %__________________________________________________________________________________________________________________
    % Skills
    \section{\mysidestyle Programming}
    Python, Bash\\
    Currently building tournament organizer website for "Magic: The Gathering" using Python and Flask.

    \section{\mysidestyle Education}

    \textbf{Montclair State University} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor of Science, Molecular Biology} \hfill \textbf{present}\vspace{-3mm}\\\vspace{-1mm}%

    \textbf{Bergen Community College} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Associate of Science, Science and Mathematics} \hfill \textbf{2009}\vspace{-3mm}\\\vspace{-1mm}%

    \section{\mysidestyle Miscellaneous Skills}
    Laboratory skills (PCR, Gel Electrophoresis, GenBank (NCBI), Compound Synthesis
      Gram Staining, Dilutions, Acid Based Titration, Gel Loading)


    %__________________________________________________________________________________________________________________
    % References
    \section{\mysidestyle References} 
    {\sl Available on request.}


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

